%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}

% personal data
\firstname{Nevroz}
\familyname{Arslan}
\address{Bleicher Str. 5}{26122 Oldenburg}    % optional, remove the line if not wanted
%\mobile{}                    % optional, remove the line if not wanted
\email{nevrozarslan@gmail.com}                      % optional, remove the line if not wanted
% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Ausbildung}
\cventry{2012--2017}{Fachbachelor Chemie}{Universität Oldenburg}{Oldenburg}{}{}
\cventry{1997--2005}{Fachbachelor Elektroingenieurwissenschaft}{Technische Universität
Istanbul}{Istanbul}{}{}
%\cvline{advisor:}{\small Professor Eric Bach}
%\cventry{2003--2007}{BS, Computer Science and Engineering}{UCLA}{Los Angeles, CA}{}{}  % arguments 3 to 6 can be left empty
%\cvline{gpa:}{\small 3.76/4.0}
%\cvline{honors:}{\small Cum Laude}


\section{Erfahrungen}

\cventry{Herbst 2012--}{Student}{Carl von Osietzky Universität Oldenburg}{Oldenburg}{}{
Organische Chemie, Naturstoffchemie, Pericyclische Reaktionen, Molekülare Strukturbestimmung, }

\cventry{Winter 2011}{Sprachstudent}{Eduglobal}{Karlsruhe}{}{
Deutschsprachkenntnis wurde verbessert.}
\cventry{Sommer 2010--Herbst 2011}{Webmaster}{}{
Selbstständig gearbeitet, die Auseinendersetzung mit der deutschen Sprache }
\cventry{Sommer 2007-- Sommer 2010 }{Programmier}{Verschiedene IT-Unternehmen}{Istanbul}{}{
www.mobilgi.com, eine Informatik Firma, für die die Supermärkte
Warenwirtschaftssysteme entwickelt hatte. Mit der Perl-Programmiersprache
habe ich die Daten bearbeitet. Datenbank(MySql) programmiert 
www.multimap.com,   
www.reidin.com,
www.parkyeri.com
}

\cventry{Frühling 2003- Herbst
  2005}{Systemadministrator}{Internet Securities International}{Istanbul}{}{
Verwaltung und Programmierung der Linux Server bei \url{http://www.securities.com}.  
}

\section{Praktische Erfahrung}
\subsection{Effiziente Nutzung}

\cvline{Programmiersprachen}{Latex, Lua, Javascript, Html, Css}
\cvline{Technologien}{ Vim, Ubuntu \& Arch Linux}

\subsection{Berufserfahrung}
\cvline{Aufgabe} {Server Administrator, Programmier} 
\cvline{Programmiersprachen}{Perl, MySql, Octave, Html }
\cvline{Technologien}{Datenbank}

\section{}
\subsection{University of California, Los Angeles}
\cvline{computer science}{Programming in C++, Digital Design, VHDL, CAD tools, Machine Language (MIPS), Computer Network Fundamentals, Physical Layer of Computer Networks, Programming Languages, Computer Architecture, Algorithms, Complexity Theory, Databases, Operating Systems, Digital Graphics}
\cvline{electrical engineering}{Electromagnetics, Semiconductors, Systems and Signals, Circuit Analysis}
\subsection{University of Wisconsin, Madison}
\cvline{computer science}{Quantum Computing, Arithmetic Algorithms, Advanced Complexity Theory, Harmonic Analysis of Boolean Functions, Computational Cognitive Science, Bioinformatics, Combinatorics, Artificial Intelligence, Advanced Databases}
\cvline{remote sensing}{Environmental Remote Sensing, Digital Image Processing}
\cvline{business}{Entrepreneurship and Small Business Management, Venture Creation}

\section{Honors}
\cvline{honor societies}{Tau Beta Pi, Eta Kappa Nu, Golden Key, Upsilon Pi Epsilon}
\cvline{dean's list}{2 semesters at UCLA}
\cvline{fellowships}{Offered Southern California's Provost Ph.D. Fellowship in Electrical Engineering}

\section{Activities}
\cventry{2004--2007}{Ultimate Frisbee Club Team}{UCLA}{Los Angeles, CA}{}{
Practiced four times a week and traveled across the western united states for between 10 and 12 tournaments each year.
}
\cventry{2007--2011}{Ultimate Frisbee Club Teams}{UW-Madison}{Madison, WI}{}{
Practiced and traveled with three Madison based ultimate frisbee club teams.
Played in numerous recreational leagues.
}
\cventry{2007--2011}{Engineers Without Borders}{UW-Madison}{Madison, WI and Orongo, Kenya}{}{
Began a long term irrigation system project to allow the members of Orongo to grow more profitable crops.
Started an income generating agroforestry project at a Kenyan Primary School.
Built and tested prototype biosand filters in both Kenya and Madison.
Built and tested prototype low cost solar cookers in both Kenya and Madison.
}
\cventry{2011-present}{Ultimate Frisbee Club Teams}{Ultimate Chicago}{Chicago, IL}{}{
Coached, captained, and played on several teams in recreational leagues.
}
\cventry{}{Other Current Hobbies}{}{}{}{
Web Programming, Camping, Hiking, Backpacking, Traveling, Road Trips, Basketball, Piano, Guitar
}

\end{document}
